Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-04-24 data_appendix_all_years.Rmd
trying to fix duplicates...still 406 extra observations somehow between the children dataset and the merge with the heads of households' characteristics

total_children <- mutate(children, id = rownames(children))

@@

```{r combining household head characteristics with children dataset}
hh_head_2 <- hh_head %>%
  select(sex, age, literacy, educ, job, tasks, pov_line, extr_pov, hh_id) %>%
  rename (female_hhhead = sex,
          hhhead_age = age,
          hhhead_literacy = literacy,
          hhhead_educ = educ,
          hhhead_job = job,
          hhhead_tasks = tasks)

total <- total_children %>%
  left_join(hh_head_2)

#total <- merge(children,hh_head_2, by="hh_id")

@@

```{r regression variable specifications}
reg_data <- total %>%
  mutate(lny = log(income))
```

>>>>

household_counts <- children %>%
group_by(hh_id) %>%
summarize(num_children = n())

children_id <- mutate(children, id = rownames(children))

total_children <- merge(children_id,household_counts, by="hh_id")

@@

```{r combining household head characteristics with children dataset}
hh_head_2 <- hh_head %>%
  select(sex, age, literacy, educ, job, tasks, pov_line, extr_pov, hh_id) %>%
  rename (female_hhhead = sex,
          hhhead_age = age,
          hhhead_literacy = literacy,
          hhhead_educ = educ,
          hhhead_job = job,
          hhhead_tasks = tasks)
total_heads_subset <- hh_head_2 %>% distinct()

#total <- total_children %>%
  #left_join(hh_head_2)
#left join command creating the duplicates problem it seems 
total <- merge(total_children,hh_head_2, by="hh_id")

total_subset <- total %>% distinct()

@@

```{r regression variable specifications}
reg_data <- total_subset %>%
  mutate(lny = log(income))
```
